Zohmg---a large scale data warehouse for aggregated time-series-based data. [DRAFT]

### 2009-05-05 doc/report/msc-report.tex
doc/report/msc-report.tex: + changed "paper" to "thesis". + added overview section.

This paper talks about a data store for aggregated multi-dimensional time-series-based data. The data is aggregated over many units of measurements and across multiple dimensions. One of these dimensions is always time.

@@

The paper is presented in three major sections: problem statement, the theoretical solution and the implementation details.

@@

>>>>

This thesis talks about a data store for aggregated multi-dimensional time-series-based data. The data is aggregated over many units of measurements and across multiple dimensions. One of these dimensions is always time.

@@

The thesis is presented in three major sections: problem statement, the theoretical solution and the implementation details.

@@

This thesis, fully, describes the Zohmg system and how to use it.

Chapter 2 the theoretical base of the problem statement is established.

In chapter 3 the tools used for the implementation are declared, moving
over to chapter 4 where the details of the implementation are presented.

How to use the Zohmg system is presented in chapter 5, while chapter 6
shows an example work flow.

Chapters 7 and 8 discusses the results, related, and future work, and
presents the conclusion, respectively.
